Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2023-06-09 doc/manuscript/ESSDmanuscript.Rmd
fix footnotes in appendix b
#39

Table B1: **Mapping of ForC fields to EFDB.** Details documented in the public GitHub repository associated with the project, IPCC-EFDB-integration repository within the ForC-db organization (file *ForC-EFDB_mapping.csv* available at [https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv](https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv)). See footnotes at end of table (STILL NEED TO BE PROPERLY INSERTED).
```{r table_ForCfieldmapping, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)

ForC_variables_included <- read.csv("figures_tables/ForC_fields_included.csv")
names(ForC_variables_included) <- stringr::str_replace_all(names(ForC_variables_included), "\\.", " ")
ForC_variables_included <- ForC_variables_included[c(1:5)] #include all fields but TO_DO

@@

```
'Required' field indicates whether the field is required by EFDB: yes = value required; (yes) = input required, missing value acceptable if not reported; auto = present within ForC infrasructure, and therefore will always be exported to EFDB ; (no) = not required for EFDB, but required for ForC and therefore will always be exported to EFDB; no = not required, but exported to EFDB when a value is present.

** '(yes)' for most recent severe disturbance; 'no' for other history events

>>>>

Table B1: **Mapping of ForC fields to EFDB.** Details documented in the public GitHub repository associated with the project, IPCC-EFDB-integration repository within the ForC-db organization (file *ForC-EFDB_mapping.csv* available at [https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv](https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv)). 
```{r table_ForCfieldmapping, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)

ForC_variables_included <- read.csv("figures_tables/ForC_fields_included.csv")
names(ForC_variables_included) <- stringr::str_replace_all(names(ForC_variables_included), "\\.", " ")
column_names <- names(ForC_variables_included) # Define column names
column_names[5] <- "Required*" # Add asterisk for footnote
names(ForC_variables_included) <- column_names# Set column names of the matrix
ForC_variables_included <- ForC_variables_included[c(1:5)]

@@

```
\* *Required* field indicates whether the field is required by EFDB: yes = value required; (yes) = input required, missing value acceptable if not reported; auto = present within ForC infrasructure, and therefore will always be exported to EFDB ; (no) = not required for EFDB, but required for ForC and therefore will always be exported to EFDB; no = not required, but exported to EFDB when a value is present.

### 2023-06-09 doc/manuscript/ESSDmanuscript.tex
fix footnotes in appendix b
#39

Table B1: \textbf{Mapping of ForC fields to EFDB.} Details documented in
the public GitHub repository associated with the project,
IPCC-EFDB-integration repository within the ForC-db organization (file
\emph{ForC-EFDB\_mapping.csv} available at
\url{https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv}).
See footnotes at end of table (STILL NEED TO BE PROPERLY INSERTED).
\begingroup\fontsize{8}{10}\selectfont

@@

\textbf{ForC table} & \textbf{ForC field} & \textbf{EFDB field} & \textbf{Usage} & \textbf{Required}\\

@@

History & date, hist.cat, hist.type & 1996 Source/Sink Categories, 2006 Source/Sink Categories, Abatement/Control technologies & used to determine distmrs.type for Source/Sink Categories, generate list of events for Abatement/Control technologies & (yes)/no**\\

@@

`Required' field indicates whether the field is required by EFDB: yes =
value required; (yes) = input required, missing value acceptable if not
reported; auto = present within ForC infrasructure, and therefore will
always be exported to EFDB ; (no) = not required for EFDB, but required
for ForC and therefore will always be exported to EFDB; no = not
required, but exported to EFDB when a value is present.

** `(yes)' for most recent severe disturbance; `no' for other history
events

>>>>

Table B1: \textbf{Mapping of ForC fields to EFDB.} Details documented in
the public GitHub repository associated with the project,
IPCC-EFDB-integration repository within the ForC-db organization (file
\emph{ForC-EFDB\_mapping.csv} available at
\url{https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/ForC-EFDB_mapping.csv}).
\begingroup\fontsize{8}{10}\selectfont

@@

\textbf{ForC table} & \textbf{ForC field} & \textbf{EFDB field} & \textbf{Usage} & \textbf{Required*}\\

@@

History & date, hist.cat, hist.type & 1996 Source/Sink Categories, 2006 Source/Sink Categories, Abatement/Control technologies & used to determine distmrs.type for Source/Sink Categories, generate list of events for Abatement/Control technologies & most recent severe disturbance: (yes) / other history events: no\\

@@

* \emph{Required} field indicates whether the field is required by EFDB:
yes = value required; (yes) = input required, missing value acceptable
if not reported; auto = present within ForC infrasructure, and therefore
will always be exported to EFDB ; (no) = not required for EFDB, but
required for ForC and therefore will always be exported to EFDB; no =
not required, but exported to EFDB when a value is present.
